Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-02-26 paper.tex
update

\texttt{f1} and \texttt{f2} call each others, and the stack will be interleaved
pushing \texttt{f1} and \texttt{f2} onto the top of current stack, but not existing 
two stack components are the same in the state space.

@@

@@

for plain direct-style, the apply handles more cases.

>>>>

\texttt{f1} and \texttt{f2} call each others, and the stack will be interleaved
pushing \texttt{f1} and \texttt{f2} onto the top of current stack, but not existing 
two stack components are identical in the state space.

@@

\begin{verbatim}
def drive_step(todo: List[State], seen: Set[State]): Set[State] = todo match {
  case Nil => seen
  case hd::tl if seen.contains(hd) => drive_step(tl, seen)
  case hd::tl =>
    val new_time = tick(hd)
    val new_states = hd match {
      case State(Let(x, App(f, ae), e), env, bstore, konts, time) 
        if isAtomic(ae) =>
        for (Clos(Lam(v, body), env_c) <- atomicEval(f, env, bstore).toList) yield {
          val frame = Frame(x, e, env)
          val baddr = allocBind(v, new_time)
          val new_env = env_c + (v -> baddr)
          val new_store = bstore.update(baddr, atomicEval(ae, env, bstore))
          State(body, new_env, new_store, frame::konts, new_time)
        }
      case State(ae, env, bstore, konts, time) if isAtomic(ae) =>
        konts match {
          case Nil => List()
          case Frame(x, e, f_env)::konts =>
            val baddr = allocBind(x, new_time)
            val new_env = f_env + (x -> baddr)
            val new_store = bstore.update(baddr, atomicEval(ae, env, bstore))
            List(State(e, new_env, new_store, konts, new_time))
        }
    }
    drive_step(new_states ++ tl, seen + hd)
}

def analyze(e: Expr): Set[State] = drive_step(List(inject(e)), Set())
\end{verbatim}

@@

for plain direct-style, the continue function handles more cases.

\begin{verbatim}
def drive_step(todo: List[State], seen: Set[State]): Set[State] = todo match {
  case Nil => seen
  case hd::tl if seen.contains(hd) => drive_step(tl, seen)
  case hd::tl =>
    val new_time = tick(hd)
    hd match {
      case State(Let(x, App(f, ae), e), env, bstore, konts, time)
        if isAtomic(ae) =>
        val closures = atomicEval(f, env, bstore).toList
        val new_states = for (Clos(Lam(v, body), env_c) <- closures) yield {
          val frame = Frame(x, e, env)
          val baddr = allocBind(v, new_time)
          val new_env = env_c + (v -> baddr)
          val new_store = bstore.update(baddr, atomicEval(ae, env, bstore))
          State(body, new_env, new_store, frame::konts, new_time)
        }
        drive_step(new_states ++ tl, seen + hd)
      case State(ae, env, bstore, konts, time) if isAtomic(ae) =>
        continue(konts, atomicEval(ae, env, bstore), bstore, new_time, tl, seen + hd)
    }
}

def continue(konts: List[Frame], ds: Set[Storable], bstore: BStore, time: Time, 
             todo: List[State], seen: Set[State]): Set[State] = 
  konts match {
    case Nil => drive_step(todo, seen)
    case Frame(x, e, f_env)::konts =>
      val baddr = allocBind(x, time)
      val new_env = f_env + (x -> baddr)
      val new_store = bstore.update(baddr, ds)
      val new_state = State(e, new_env, new_store, konts, time)
      drive_step(new_state::todo, seen)
  }
\end{verbatim}
